Formulating and Validating RDF Constraints Generically

### 2014-12-29 paper/RDF validation requirements/RDF validation requirements.tex
Context-Specific Exclusive OR of Property Groups
evaluation

\begin{gcotable}
property & $\exists$ laserSwordColor . LaserSwordColor & laserSwordColor & - & LaserSwordColor & $\exists$ & - \\
class & Jedi & - & - & $\exists$ laserSwordColor . LaserSwordColor & $\neg$ & - \\
class & LaserSwordColor & - & - & $\{blue\}$, $\{green\}$, $\{white\}$ & $\sqcup$ & - \\
\end{gcotable}

@@

@@

@@

@@

@@

I'm not sure about the meaning of this constraint, but for me this seams like e.g. the range of a role... but if this is the case, take into account the consequences of reasoning with OWA...

@@

I'm not sure about the meaning of this constraint, but for me this seams like e.g. the domain of a role... but if this is the case, take into account the consequences of reasoning with OWA...

@@

\begin{DL}
Not Expressible in DL!
\end{DL}

@@

\begin{itemize}
	\item R-68-REQUIRED-PROPERTIES
\end{itemize}

@@

@@

@@

\begin{itemize}
	\item R-69-OPTIONAL-PROPERTIES
\end{itemize}

@@

@@

>>>>

\begin{gcotable}
property & $\exists$ laserSwordColor . LaserSwordColor & laserSwordColor & - & LaserSwordColor & $\exists$ & - \\
class & Sith & - & - & $\exists$ laserSwordColor . LaserSwordColor & $\neg$ & - \\
class & LaserSwordColor & - & - & $\{blue\}$, $\{green\}$, $\{white\}$ & $\sqcup$ & - \\
\end{gcotable}

@@

Define the order of the property \ms{listElement} for the class \ms{rdf:List}.
List elements are of datatype \ms{xsd:string}.

@@

\begin{gcotable}
property & rdf:List & listElement & - & xsd:string & order & 1 \\
\end{gcotable}

@@

The length of strings of the property \ms{hasISBN} for the context class \ms{Book} must be exactly 3.

@@

\begin{gcotable}
property & Book & hasISBN & - & xsd:string & length & 3 \\
\end{gcotable}

@@

Within the context \ms{AP} (application profile) the classes \ms{Book} and \ms{Paper} are valid.

\begin{gcotable}
class & AP & - & - & Book, Paper & context-specific valid classes & true \\
\end{gcotable}

@@

Within the context \ms{AP} (application profile) the properties \ms{dcterms:subject} and \ms{dcterms:title} are invalid.

\begin{gcotable}
property & AP & dcterms:subject, dcterms:title & - & - & context-specific valid properties & false \\
\end{gcotable}

@@

Calculate rectangle areas.

\begin{gcotable}
property & Rectangle & area & width, height & xsd:integer & multiplication & - \\
\end{gcotable}

@@

\ms{Required Properties} corresponds to the requirement \ms{R-68-REQUIRED-PROPERTIES}.

@@

For persons the property \ms{hasAncestor} has to be stated pointing to persons.

@@

\begin{gcotable}
property & Person & hasAncestor & - & Person & $\exists$ & - \\
\end{gcotable}

@@

\ms{Optional Properties} corresponds to the requirement \ms{R-69-OPTIONAL-PROPERTIES}.

@@

For persons the property \ms{hasAncestor} pointing to persons is optional.

@@

\begin{gcotable}
property & $\exists$ hasAncestor.Person & hasAncestor & - & Person & $\exists$ & - \\
class & Person & - & - & $\exists$ hasAncestor.Person & $\sqsubseteq$ & - \\
\end{gcotable}

\begin{gcotable}
property & Person & hasAncestor & - & Person & optional & - \\
\end{gcotable}

### 2014-12-29 paper/paper 2/paper 2.tex
evaluation

@@

\ms{Complex constraints} encompass complex constraints and \ms{simple constraints} (atomic constraints).
DL statements of complex constraints are created out of DL statements of composed constraints.

@@

\textbf{Context-Specific Exclusive OR of Property Groups.}
\begin{gcotable}
class & Half-Klingon & - & - & E, F & XOR \\
class & E & - & - & A, B & $\sqcap$ \\
class & F & - & - & C, D & $\sqcap$ \\
property & A & klingonMother & - & Klingon & = & 1 \\
property & B & humanFather & - & Human & = & 1 \\
property & C & humanMother & - & Human & = & 1 \\
property & D & klingonFather & - & Klingon & = & 1 \\
\end{gcotable}

@@

\section{Constraints Expressible in DL}

\section{Constraints Not Expressible in DL}

There are constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.

% maybe additional constraint default values:
% ear shape of races, e.g. vulcans / teeth color

@@

>>>>

\newenvironment{evaluation}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
	\begin{center}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

@@

\ms{Complex constraints} encompass complex constraints and/or \ms{simple constraints} (atomic constraints).
DL statements of complex constraints are created out of DL statements of composed constraints.

@@

@@

\section{Simple Constraints Not Expressible in DL}

There are simple constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.

% maybe additional constraint default values:
% ear shape of races, e.g. vulcans / teeth color
% mathematical operations

@@

\section{Evaluation}

We evaluated to which extend the most promising five constraint languages fulfill each requirement to formulate RDF constraints \cite{BoschNolleAcarEckert2015}.
If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint.
If a constraint cannot be expressed in DL, we added a mapping to the generic constraint.
Therefore, we show that each constraint can be mapped to a generic constraint.

\begin{evaluation}
\ms{Expr-C} (41) & 6 & 18(4) & 7(4) & 8 & 12 & 40(1)\\
\ms{Expr-R} (33) & 8 & 29 & 11 & 11(2) & 11(1) & 33 \\ 
\end{evaluation}
